My title

### 2024-11-03 paper/paper.qmd
Update paper.qmd
Add estimand description

>>>>

The estimand in this study represents the expected level of voter support for each primary candidate, Kamala Harris and Donald Trump, based on aggregated polling data across diverse demographics and polling methodologies. This measure aims to capture the central tendency of public opinion, adjusted for polling reliability and sample characteristics, to provide a stable estimate of each candidate's projected support under current conditions. By centering on this estimand, the analysis offers a robust and interpretable forecast applicable for strategic decision-making in both political and economic contexts.
